---
title: "GTM Strategy Analytics Report"
author: "Satya Panda"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(readr)
library(dplyr)
library(ggplot2)
```

# Executive Summary
This report delivers a segment-wise analytics view of your Go-To-Market (GTM) Strategy Framework. By breaking down the GTM pillars into actionable segments, you gain clarity on focus areas, gaps, and opportunities for each strategic component.

# Introduction
This report analyzes the GTM Strategy Framework by segmenting tasks under each GTM pillar, providing targeted insights for data-driven decision-making.

# Data Import

```{r}
gtm_data <- read_csv("GTM_Strategy_Framework.csv")
gtm_data
```

# Data Summary & Insights

```{r}
# Show structure and a sample of the data for context
glimpse(gtm_data)
kable(head(gtm_data, 5), caption = "Sample of GTM Strategy Tasks")
```

- **Observation:** The framework covers all major GTM pillars, ensuring a balanced approach across market analysis, value delivery, competition, sales, marketing, customer success, and feedback.

# Data Preparation: Segmenting GTM Tasks

```{r}
# Convert data to long format for segment-wise analysis
gtm_long <- gtm_data %>%
  mutate(Segment = row_number()) %>%
  tidyr::pivot_longer(-Segment, names_to = "Component", values_to = "Task") %>%
  filter(Task != "")

# Show a sample of the segmented data
kable(head(gtm_long, 10), caption = "Segmented GTM Tasks")
```

# Segment-wise Task Distribution

```{r}
# Count tasks per segment and component
segment_summary <- gtm_long %>%
  group_by(Segment, Component) %>%
  summarise(Task_Count = n(), .groups = 'drop')

# Visualize segment-wise distribution
library(ggplot2)
ggplot(segment_summary, aes(x = Component, y = Task_Count, fill = as.factor(Segment))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme_minimal() +
  labs(title = "Segment-wise Distribution of GTM Tasks", x = "GTM Component", y = "Number of Tasks", fill = "Segment")
```

- **Insight:** This visualization shows how each GTM segment (row) contributes to the overall framework, highlighting strengths and gaps by component.

# Deep Dive: Segment Profiles

```{r}
# Profile each segment by listing its tasks
gtm_profiles <- gtm_long %>%
  group_by(Segment) %>%
  summarise(Tasks = paste0(Component, ": ", Task, collapse = "; "))
kable(gtm_profiles, caption = "GTM Segment Profiles")
```

- **Interpretation:** Review each segment’s profile to ensure all critical GTM activities are covered and aligned with your strategy.

# Recommendations
- **Segment Focus:** Address any segments with fewer tasks to ensure comprehensive coverage.
- **Strategic Alignment:** Use segment profiles to align team responsibilities and track progress.
- **Continuous Review:** Regularly update segment tasks as your GTM strategy evolves.

# Conclusion
This segment-wise analytics report provides a granular view of your GTM framework, enabling targeted improvements and strategic clarity for each pillar and segment.
